Taking Dyads Seriously

### 2018-01-29 paper/coverletter/netsMatter_coverLetter.tex
sync up

{Editorial Team of Political Analysis via submission portal}

@@

We evaluate the utility of the AME framework using a simulation based exercise and a replication of five recently published works from the field of International Relations. Through the simulation exercise, we show that in the presence of unobserved dependencies the model is able to still provide less biased estimates and better calibrated standard errors than extant approaches in the literature. Next, for almost each of the replications reestimated using the AME framework we find that the case for the key findings from the original works become much less compelling. Additionally, we show through an out-of-sample cross-validation exercise that the AME approach uniformly outperforms each of the replicated approaches in capturing the data generating process of the event of interest.\\[1ex]

>>>>

{Editorial Team of American Political Science Review via submission portal}

@@

We evaluate the utility of the AME framework using a simulation based exercise and a replication of five recently published works from the field of International Relations. Through the simulation exercise, we show that in the presence of unobserved dependencies the model is able to provide less biased estimates and better calibrated standard errors than extant approaches in the literature. Next, for nearly all of the replications reestimated using the AME framework we find that the case for the key findings from the original works become much less compelling. Additionally, we show through an out-of-sample cross-validation exercise that the AME approach uniformly outperforms each of the replicated approaches in capturing the data generating process of the event of interest.\\[1ex]
